---
title: "Lab 3"
author: "Cecilia Millane"
date: "2/15/2018"
output: html_document
---

```{r}
#install.packages('productplots')
data(happy, package="productplots")
head(happy)
```

### Data Cleaning

<<<<<<< isaacdev
```{r}
suppressMessages(library(tidyverse))
HAPPY <- HAPPY %>% mutate(DEGREE = replace(DEGREE, DEGREE %in% c("NA", "DK", "IAP"), NA))
```

```{r}
HAPPY$AGE[HAPPY$AGE %in% "89 OR OLDER"] <- 89
HAPPY <- HAPPY %>% mutate( DEGREE = factor(DEGREE, 
                                           levels=c("LT HIGH SCHOOL", 
                                                            "HIGH SCHOOL", 
                                                            "JUNIOR COLLEGE",
                                                            "BACHELOR", "GRADUATE")))

```
```{r}
str(HAPPY)
```

```{r}
columns_to_factor <- c("YEAR","MARITAL","SEX","HEALTH")
HAPPY2 <- HAPPY %>%
            mutate_each_(funs(factor(.)),columns_to_factor)
```
```{r}
str(HAPPY2)
```
=======
2. Variable Type

```{R}
HAPPY$AGE[HAPPY$AGE %in% "89 OR OLDER"] <- 89
```

3. Order
```{R}
HAPPY <- HAPPY %>% mutate( DEGREE = factor(DEGREE, levels=c("LT HIGH SCHOOL", "HIGH SCHOOL", "JUNIOR COLLEGE", "BACHELOR", "GRADUATE")))
HAPPY <- HAPPY %>% mutate( HAPPY = factor(HAPPY, levels=c("NOT TOO HAPPY", "PRETTY HAPPY", "VERY HAPPY")))
```


```{r cars}
summary(cars)
```
>>>>>>> master